Cartogram Mapping and Application to Cancer Data.

### 2019-06-26 review_article.Rmd
CPISACA additions

Choropleth mapping methods effectively explore a relationship across a geographical space. 
Thematic maps involve drawing administrative or other boundaries and filling the regions with colours, symbols or patterns to present levels, or rates, of the information communicated. @CIBMUK believes these 'representations are highly intuitive' as the familiar shapes help those looking at the maps to visually infer spatial relationships. Using the topography as a base map is common for thematic maps of phenomena [@CD].
The visualisations are true maps, used for visual inspection and can help to direct hypotheses about the spatial patterns across the physical space. 
These true maps rely on visual perception, a fallible metric as it can cause viewers to 'weight the shades from the largest areas more heavily.' The inferences derived from visual inspection, and the hypotheses developed can suffer from 'bias'. The use of thematic disease mapping was motivated by a 'desire to evaluate geographical patterns' @DMAHP. This technique has been seen as a 'trigger for questions' which drives research of spatial distributions of diseases. @MACM also recognise the intuition that can be derived from choropleths with the critique that they must be 'validated by rigorous statistical analyses.'

@@

@@

In theory these ideas have been used, but the people making them do not necessarily have not access or ability to create them.

Therefore the uptake of these maps has been due to education, not the validity of their use.

@@

@@

 @ECGC present the problem of maintaining shape presevation in non-contiguous cartograms.

@@

@CVBGSD presents bivariate maps, using size and colour for different variables.

@@

@@

>>>>

Choropleth mapping methods effectively explore a relationship across a geographical space. 
Thematic maps involve drawing administrative or other boundaries and filling the regions with colours, symbols or patterns to present levels, or rates, of the information communicated. @CIBMUK believes these 'representations are highly intuitive' as the familiar shapes help those looking at the maps to visually infer spatial relationships. Using the topography as a base map is common for thematic maps of phenomena [@CD].
The visualisations are true maps, used for visual inspection and can help to direct hypotheses about the spatial patterns across the physical space. 
These true maps rely on visual perception, a fallible metric as it can cause viewers to 'weight the shades from the largest areas more heavily.' The inferences derived from visual inspection, and the hypotheses developed can suffer from 'bias'. The use of thematic disease mapping was motivated by a 'desire to evaluate geographical patterns' @DMAHP. This technique has been seen as a 'trigger for questions' which drives research of spatial distributions of diseases. @CPISACA recommends Choropleths, or isopleths for 'measures that are continuous over space, such as elevation or temperature.' @MACM also recognise the intuition that can be derived from choropleths with the critique that they must be 'validated by rigorous statistical analyses.'

@@

<!--
@CPISACA
The potential audience for the results of a spatial analysis of health data is no longer limited to scientists but now also includes the public, policymakers, the media, and a host of others.

Using the recognisable geography, that is familiar, helps communicate the information.
-->

@@

@@

 @ECGC also present the problem of maintaining shape presevation in non-contiguous cartograms.

@@

@@

@@

<!--
@CVBGSD presents bivariate maps, using size and colour for different variables. 
-->

@MDAC define the term 'mosaic cartograms'. 
Compare amount of tiles to contrast population of regions.
'Cartograms show a data value per input region by scaling each region such that its area is proportional to its data value. Mosaic cartograms show data in multiples of tiles, hence the input data must consist of, or be cast into, small integer units.'

@@

>designing a map tailored to precise goals [is] easier than forcing a single map to accommodate diverse objectives - @CPISACA

With that in mind, the intented user and message to communicate should drive map selection.

'Where control of the message is important, static maps will continue to be the most effective, although good tables, graphs, and explanatory text are still needed in order to ensure that different people will see the same thing in the maps' @CPISACA

<!-- @CPISACA contrasted several online atlases in a 2006 paper, consider for structure? -->
